Extended Data

### 2021-11-16 doc/manuscript/Dow_manuscript_Nature.Rmd
edit Fig. 1 legend
@camerondow35 , I removed "(determined by whether the posterior credible interval included 0 or not)" from the Fig. 1 legend. I think that's a detail that can be specified in the methods. But let me know if you have reason to feel strongly about this.

![**Figure 1 | Summary of tree growth changes under warmer spring temperatures.** (a) Schematic illustrating parameters of interest and summarizing how each responds to warmer maximum temperatures during a 'critical temperature window', defined as the period with the strongest control over $DOY_{25}$; (b) Variable definitions and summary responses to warmer spring temperatures at two temperate forests and for two groups of broadleaf deciduous species (RP=ring porous; DP=diffuse porous), where up and down arrows indicate significant (determined by whether the posterior credible interval included 0 or not) increases and decreases, respectively, '-' indicates no significant correlation, and 'mixed' indicates a mix of significant and non-significant correlations, often in different directions.](tables_figures/schematic_summary_with_table.png){ width=70% }

>>>>

![**Figure 1 | Summary of tree growth changes under warmer spring temperatures.** (a) Schematic illustrating parameters of interest and summarizing how each responds to warmer maximum temperatures during a 'critical temperature window', defined as the period with the strongest control over $DOY_{25}$; (b) Variable definitions and summary responses to warmer spring temperatures at two temperate forests and for two groups of broadleaf deciduous species (RP=ring porous; DP=diffuse porous), where up and down arrows indicate significant increases and decreases, respectively, '-' indicates no significant correlation, and 'mixed' indicates a mix of significant and non-significant correlations, often in different directions.](tables_figures/schematic_summary_with_table.png){ width=70% }
